Applying State-free Reversible VAMPNets and Markov State Models to Learn Dynamics of DNA Oligonucleotides

### 2020-09-26 manuscript.tex
Updates from Overleaf

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The document title should be given as usual. Some journals require
%% a running title from the author: this should be supplied as an
%% optional argument to \title.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title[]{Investigating DNA d}

@@

The GC-mix sequence shows a similar implied timescale distribution to GC-core, however we no longer see a converged slow mode corresponding to multi-base fraying behavior. Instead, we observed two modes converge, corresponding to the association/dissociation dynamic and diffusive behavior while strands are dissociated. These correlate closely with the first and third GC-core SRV modes. Although we built our SRV-MSM using these two coordinates, we again were unable to form a stable third state along the second coordinate. As such, we designated this transitions as effectively two-state within the resolution of our model, however we do observe substantial fraying of the two AT termini in the simulation data. Although these frayed states may be too short-lived to resolve a distinct slow mode, this behavior shows qualitative agreement with experimental analysis of this sequence attributing fraying prior to dissociation as a deviation from all-or-nothing behavior \citep{Sanstead2016}.  While AT-termini fraying is surely a prerequisite to dissociation, we find these states to be so common and fleeting that very few progress to full dissociation. On the other hand, the 4bp-frayed state in GC-core had a substantial probability (~10\%) of fully dissociated rather reforming an intact helix. Furthermore, one or two base pair fraying does not fundamentally disrupt the helix in such a way that its re-formation is kinetically inhibited by the intermediate structures we present for GC-core.

@@

	\item Track GC-mid trajectories along transition region
	\item Discuss misaligned configurations here instead of in the GC-core section
\end{enumerate}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The document title should be given as usual. Some journals require
%% a running title from the author: this should be supplied as an
%% optional argument to \title.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title[]{Applying State-free Reversible VAMPNets and Markov State Models to Learn Dynamics of DNA Oligonucleotides}

@@

The GC-mix sequence shows a similar implied timescale distribution to GC-core, however we no longer see a converged slow mode corresponding to multi-base fraying behavior. Instead, we observed two modes converge, corresponding to the association/dissociation dynamic and diffusive behavior while strands are dissociated. These correlate closely with the first and third GC-core SRV modes. Although we built our SRV-MSM using these two coordinates, we again were unable to form a stable third state along the second coordinate. As such, we designated this transitions as effectively two-state within the resolution of our model, however we do observe substantial fraying of the two AT termini in the simulation data. Although these frayed states may be too short-lived to resolve a distinct slow mode, this behavior shows qualitative agreement with experimental analysis of this sequence which attributed fraying prior to dissociation as a deviation from all-or-nothing behavior \citep{Sanstead2016}.  While AT-termini fraying is surely a prerequisite to dissociation, we find these states to be so common and fleeting that very few progress to full dissociation. On the other hand, the 4bp-frayed state in GC-core had a substantial probability (~10\%) of fully dissociated rather reforming an intact helix. Furthermore, one or two base pair fraying does not fundamentally disrupt the helix in such a way that its re-formation is kinetically inhibited by the intermediate structures we present for GC-core.

@@

	\item Track GC-mix trajectories along transition region
	\item Discuss misaligned configurations here instead of in the GC-core section
\end{enumerate}
